\mytitle

### 2015-08-04 MSc_diss.tex
Updates in mean ANs mixing ratios (before renaming ANs)

\documentclass[11pt,a4paper]{article}
% Encoding and language
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
% Colors
\usepackage[usenames,dvipsnames]{color}
\usepackage{colortbl}
% Paper size and margins
%\usepackage{rotating}
\usepackage{pdflscape}
%\usepackage[a4paper,showframe]{geometry}
\usepackage{vmargin}
\setmarginsrb{2cm}{2cm}{2cm}{2cm}{0cm}{0cm}{0cm}{1.5cm}
\usepackage{pdflscape}
\usepackage{afterpage}
% Indenting
\usepackage{indentfirst}
%\setlength{\parindent}{1cm}
\setlength{\parskip}{0.5cm}
% Symbols
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
% Equations
\usepackage{eulervm} % upright font in eqns (Palatino)
\usepackage{cool}
\usepackage{mathtools} % for arrows
\renewcommand{\theequation}{R\arabic{equation}}
% References
\usepackage{natbib}
\bibliographystyle{apalike}
% Hyperlinks and labels
%\usepackage{showkeys}
\usepackage[linktocpage=true,plainpages=false,pdfpagelabels=false]{hyperref}
\definecolor{citecolor}{rgb}{0.2,0.7,0.9}
\definecolor{urlcolor}{rgb}{0,0,1}
\hypersetup{
    colorlinks, linkcolor={Blue},
    citecolor={Blue}, urlcolor={Black}
}
% Figures
\usepackage{subcaption}
\usepackage{alphalph}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usepackage{epstopdf}
% Tikz styles
\tikzstyle{reg} = [rounded rectangle, text width=2cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
\tikzstyle{rad} = [rounded rectangle, draw=none, text width=2cm, fill=red!10, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
\tikzstyle{long} = [rounded rectangle, draw=none, text width=3.5cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]   
\tikzstyle{add} = [scale=1.5, draw=none,fill=none,align=center]
\tikzstyle{emp} = [draw=none,fill=none]
\tikzstyle{ar} = [->,draw=black!70,line width=2]
\tikzstyle{ln} = [-,draw=black!70,line width=2]
% Title etc
\newcommand{\mytitle}{Investigation of the relationship between tropospheric ozone production efficiency and carbon bond emissions}
\newcommand{\authorname}{Maria Zamyatina}
\newcommand{\authornumber}{Student No: 100106685}
\newcommand{\degname}{Master of Science}
\newcommand{\univname}{University of East Anglia}
\newcommand{\univaddr}{University Plain \\ Norwich NR47TJ UK}
\newcommand{\depname}{School of Environmental Sciences}
\newcommand{\mydate}{\the\year}

@@

MAKE GRAPHIC FROM TABLE ABOUT O3 BUDGETS!

@@

\subsubsection*{Mean AN concentrations}
\begin{table}
\begin{tabular}{cccc}
\hline
Environment   & Mean $RONO_2$ mixing ratio                & $RONO_2$ breakdown & Reference \\
\hline
ITOP?         & mean $\Sigma RONO_2$ 10 ppt               &          & \citep{Reeves2007} \\
???           & mean $\Sigma RONO_2$ 14 ppt               &          & \citep{Roberts1998} \\
remote marine & 2-butyl and 2- and 3-pentyl: 0.8-37 pptv & &\citep{Atherton1989} [Atlas, 1988]\\
urban         & 2-butyl and 2- and 3-pentyl?: approx. 2 ppb & & \citep{Atherton1989} [Hanst et al., 1982] \\
??                         & MeONO2: 1.2 to 43 pptv     &          & \citep{Chuck2002} \\
??                         & EtONO2: 0.8 to 10 pptv     &          & \citep{Chuck2002} \\
remote marine & MeONO2: 0.2 to 50 pptv     & in lit. (2, 8, 9) & \citep{Chuck2002} \\
remote marine & EtONO2: 0.3 to 12.2 pptv   & in lit. (2, 8, 9) & \citep{Chuck2002} \\
Pacific Ocean & MeONO2: 50 pptv            &                   & \citep{Blake2003} \\
airborne      & $\Sigma RONO_2$: approx 1 ppb         & difference between NOy and (NOx+PAN+HNO3) 
                                                        is sample closest to the plume center & \citep{Neuman2012} \\
rural         & mean $\Sigma RONO_2$ (C1-C8): range: 30-630 ppt, mean over the whole period 120 ppt & & \citep{Flocke1998} \\
\hline
\end{tabular}
\end{table}

>>>>

\documentclass[11pt,a4paper]{article}
% Encoding and language
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
% Colors
\usepackage[usenames,dvipsnames]{color}
\usepackage{colortbl}
% Paper size and margins
%\usepackage{rotating}
\usepackage{pdflscape}
%\usepackage[a4paper,showframe]{geometry}
\usepackage{vmargin}
\setmarginsrb{2cm}{2cm}{2cm}{2cm}{0cm}{0cm}{0cm}{1.5cm}
\usepackage{pdflscape}
\usepackage{afterpage}
% Indenting
\usepackage{indentfirst}
%\setlength{\parindent}{1cm}
\setlength{\parskip}{0.5cm}
% Symbols
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
% Equations
\usepackage{eulervm} % upright font in eqns (Palatino)
\usepackage{cool}
\usepackage{mathtools} % for arrows
\renewcommand{\theequation}{R\arabic{equation}}
% References
\usepackage{natbib}
\bibliographystyle{apalike}
% Hyperlinks and labels
%\usepackage{showkeys}
\usepackage[linktocpage=true,plainpages=false,pdfpagelabels=false]{hyperref}
\definecolor{citecolor}{rgb}{0.2,0.7,0.9}
\definecolor{urlcolor}{rgb}{0,0,1}
\hypersetup{
    colorlinks, linkcolor={Blue},
    citecolor={Blue}, urlcolor={Black}
}
% Figures
\usepackage{subcaption}
\usepackage{alphalph}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\usepackage{epstopdf}
% Tables
\usepackage{multirow}
% Tikz styles
\tikzstyle{reg} = [rounded rectangle, text width=2cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
\tikzstyle{rad} = [rounded rectangle, draw=none, text width=2cm, fill=red!10, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
\tikzstyle{long} = [rounded rectangle, draw=none, text width=3.5cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]   
\tikzstyle{add} = [scale=1.5, draw=none,fill=none,align=center]
\tikzstyle{emp} = [draw=none,fill=none]
\tikzstyle{ar} = [->,draw=black!70,line width=2]
\tikzstyle{ln} = [-,draw=black!70,line width=2]
% Title etc
\newcommand{\mytitle}{Investigation of the relationship between tropospheric ozone production efficiency and carbon bond emissions}
\newcommand{\authorname}{Maria Zamyatina}
\newcommand{\authornumber}{Student No: 100106685}
\newcommand{\degname}{Master of Science}
\newcommand{\univname}{University of East Anglia}
\newcommand{\univaddr}{University Plain \\ Norwich NR47TJ UK}
\newcommand{\depname}{School of Environmental Sciences}
\newcommand{\mydate}{\the\year}

@@

@@

\begin{table}%[ht] % mean AN mixing ratios
\begin{tabular}{cccc}
\hline
Environment     & Mean $\Sigma RONO_2$ & $\Sigma RONO_2$ breakdown & Reference \\
\hline
remote marine   & 10 pptv    & methyl                   & \citep{Reeves2007} \\
(North Atlantic)&            & ethyl                    & \\
airborne        &            & 1-propyl                 & \\   
                             && 2-propyl                & \\   
                             && 2-butyl                 & \\                                                                                               
                             && 2-methyl-3-butyl        & \\
                             && sum of 2- and 3-pentyl  & \\
\hline
rural           & 14 pptv    & methyl                   & \citep{Roberts1998} \\
(Nova Scotia, Canada)        &&  ethyl   & \\
stationary                   && n-propyl & \\
Chebogue Point               && 2-propyl & \\
                             && 2-butyl  & \\ 
\hline
rural         & 120 ppt (30-630 ppt) & $C_1$-$C_8$       & \citep{Flocke1998} \\
(Black Forest, Germany)      &&& \\ 
stationary                   &&& \\
\hline
polluted marine & approx 1 ppb        & $NO_y$-($NO_x$+$HNO_3$+$PAN$) & \citep{Neuman2012} \\
(Gulf of Mexico)&(plume center) && \\
airborne &&& \\
\hline
\end{tabular}
\end{table}
%??                         & MeONO2: 1.2 to 43 pptv     &          & \citep{Chuck2002} \\
%??                         & EtONO2: 0.8 to 10 pptv     &          & \citep{Chuck2002} \\
%remote marine & MeONO2: 0.2 to 50 pptv     & in lit. (2, 8, 9) & \citep{Chuck2002} \\
%remote marine & EtONO2: 0.3 to 12.2 pptv   & in lit. (2, 8, 9) & \citep{Chuck2002} \\
%Pacific Ocean & MeONO2: 50 pptv            &                   & \citep{Blake2003} \\
